---
title: "Fish and health in Finland and Porvoo: results with special focus on PFAS compounds"
author: "Jouni Tuomisto"
date: "2021-03-15"
output: html_document
params:
  N: 200
  porvoo: TRUE
---
## Shortcut to model download

This is an open assessment looking at health effects of fish consumption in Finland. The details of the assessment are described at [Opasnet](http://fi.opasnet.org/fi/PFAS-yhdisteiden tautitaakka). This file contains the R code to run the assessment model.

This code downloads all the ovariables created by the previous code, fishhealth_initiate.Rmd, runs the model and plots various graphs and tables about the results.

These problems have been fixed:

2. Calculate total personal BoD for individuals in Porvoo and Helsinki. Do not compare those at the (Finnish) population level. DONE
3. Correct the fish intake distribution to manage dimension Area correctly. DONE
4. Check that all oapply NA-fillings are intended. DONE
5. Correct the "Kalansyönti Suomessa keskimäärin" figure. DONE
6. PFOS, PFAS: ug/g --> ng/g DONE
7. PFAS: separate Porvoo from other regions. DONE
8. NOTE! Salmon concentrations include farmed salmon at the moment. This is OK for health impact assessment. DONE
9. Is amount / Group good for fillna? check. Solution: Yes, because Inpamount does not contain Group. DONE
10. Is expo_locations still used? Yes. DONE 
11. Kalansyönti väestössä: Group is not ordered correctly. DONE
12. Yhdisteiden saanti kalasta: Too many averages. Are they gender-specific? Solution: match with Area. DONE
13. Exposure to compounds: thin the Age on x axis. DONE
14. BoDattr tables: orbind the summary row to each table. DONE
15. Amount for Porvoo is too high. Why? Solution: Food causes multiplication, so clarify Inpamount. DONE
16. Hg produces NA in some cases. Why? Solution: remove rows with NA. DONE

These issues are to be fixed:

17. Abraham et al 2020 kynnystason lisäys annos-vasteeseen DONE
18. taulukko terveysvaikutuksista altisteet ja terveysvasteet DONE
19. Kuva 1: pallokuva kokonaistautitaakasta (vanha kuva 6) DONE
20. Kuva 2: ikäjakauma nettoterveysvaikutuksesta (vanha kuva 7 ilman vasteita) DONE
21. Kuva 3: Venn-kuvaaja TWI vs RDI DONE
22. Kuva 4 syönti: suomi vs Porvoo, ei sukupuolia. suomenna DONE
23. Kuva 5 PFAS-altistus Suomi, Helsinki, Porvoo DONE
24. Kuva 6 kaikkien aineiden altistus. Lisää kalan syöntisuositus. Kuva 4*2, korkeampi. suomenna DONE
25. Suomenna kaikki kuvat ja taulukot. DONE


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) 

# This is code Op_fi7797/ on page [[PFAS-yhdisteiden tautitaakka]]

library(OpasnetUtils) # Install the newest version from https://github.com/jtuomist/OpasnetUtils not from CRAN.
library(tidyverse)
library(thlGraphs)
library(plotly)
library(readxl)
library(reshape2)
library(ggVennDiagram)
library(ggforce)

openv.setN(params$N)

lang <- data.frame(
  en=c(
  "Fish",
  "Average fish",
  "Bream",
  "Flounder",
  "Herring",
  "Perch",
  "Roach",
  "Salmon",
  "Whitefish",
  "Group",
  "Toddlers",
  "Other children",
  "Adolescents",
  "Adults",
  "Elderly",
  "Area",
  "Finland",
  "Porvoo",
  "Exposure_agent",
  "DHA",
  "MeHg",
  "Omega3",
  "PFAS",
  "TEQ",
  "Vitamin D",
  "Type",
  "RDI",
  "TDI",
  "Response",
  "All-cause mortality",
  "CHD2 mortality",
  "Loss in child's IQ points",
  "Depression",
  "Vitamin D recommendation",
  "Breast cancer",
  "Immunosuppression",
  "Yes or no dental defect",
  "Sperm concentration",
  "Cancer morbidity yearly",
  "Age"
),
fi=c(
  "Kala",
  "Keskiarvokala",
  "Lahna",
  "Kampela",
  "Silakka",
  "Ahven",
  "Särki",
  "Lohi",
  "Siika",
  "Ryhmä",
  "Taapero",
  "Lapsi",
  "Nuori",
  "Aikuinen",
  "Ikääntynyt",
  "Alue",
  "Suomi",
  "Porvoo",
  "Altiste",
  "DHA",
  "Metyylielohopea",
  "Omega-3",
  "PFAS",
  "Dioksiini",
  "D-vitamiini",
  "Päiväsaanti",
  "Suositeltu",
  "Siedettävä",
  "Vaikutus",
  "Kokonaiskuolleisuus",
  "Sydänkuolleisuus",
  "Älykkyysosamäärä",
  "Masennus",
  "D-vitamiinisuositus",
  "Rintasyöpä",
  "Vastustuskyky",
  "Hammasvaurio",
  "Hedelmättömyys",
  "Syöpäsairastuvuus",
  "Ikä"
))
la <- function(x) {
  rp <- function(txt) {
      tst <- match(txt, lang$en)
      txt <- ifelse(is.na(tst),txt,lang$fi[tst])
      return(txt)
  }
  if("ovariable" %in% class(x)) out <- x@output else out <- x

  colnames(out) <- rp(colnames(out))
  for(i in 1:ncol(out)) {
    if(is.factor(out[[i]])) levels(out[[i]]) <- rp(levels(out[[i]]))
    if(is.character(out[[i]])) out[[i]] <- rp(out[[i]])
  }
  if("ovariable" %in% class(x)) x@output <- out else x <- out
  return(x)
}

```


```{r load model}

params

objects.latest("Op_fi5932",code_name="initiate") # [[PFAS-yhdisteiden tautitaakka]]

# Update decisions and collapses so that you don't need to initiate the whole model if you build new scenarios.
dec <- opbase.data("Op_fi5932", subset="Decisions")[-1] 
DecisionTableParser(dec)

CTable <- opbase.data("Op_fi5932",subset="CollapseMarginals")
if(!params$porvoo) CTable <- CTable[CTable$Variable!="expo_dir" | CTable$Function!="sample" , ]
CollapseTableParser(CTable)
CTable

```

```{r run model}

conc_eukalat <- EvalOutput(conc_eukalat)
BoDattr <- EvalOutput(BoDattr, verbose=TRUE)

```

```{r summary tables}
if(FALSE) {
oprint(summary(amount,"mean"))
oprint(summary(BoD,marginals=c("Age","Response"),"mean"))
oprint(summary(BoD,marginals=c("Gender","Response"),"mean"))
summary(BoDattr)
oprint(summary(BoDattr,marginals=c("Age","Response"),"mean"))
oprint(summary(BoDattr,marginals=c("Exposure_agent","Response"),"mean"))
oprint(summary(BoDattr,marginals=c("Gender","Response"),"mean"))
oprint(summary(case_burden,"mean"))
oprint(summary(conc,"mean"))
oprint(summary(dose,"mean"))
oprint(summary(ERF,"mean"))
oprint(summary(expo_dir,"mean"))
oprint(summary(expo_dir,marginals="Exposure_agent"))
oprint(summary(expo_indir,"mean"))
oprint(summary(exposure,"mean"))
#oprint(summary(fish_proportion,"mean"))
oprint(summary(incidence,"mean"))
oprint(summary(PAF,"mean"))
oprint(summary(population,"mean"))
oprint(summary(RR,"mean"))
}

```


```{r plots}
###################
# Graphs
amount$Group <- factor(amount$Group, levels=c("Infants","Toddlers","Other children","Adolescents",
                                        "Adults", "Elderly"))

tmp <- oapply(amount,NULL,mean,"Gender")
tmp <- la(tmp[tmp$Area!="Helsinki",])

p <- ggplot(trim(tmp), aes(x=Ryhmä, weight=amountResult, fill=Kala))+geom_bar()+
  coord_flip()+ facet_grid(Alue ~ .)+
  thlTheme()+
  labs(
    title="Kalansyönti Suomessa ja Porvoon
    vapaa-ajankalastajilla ikäryhmittäin",
    subtitle="Syönti (g/d)"
  )
print(p)
ggsave("Kalansyönti Suomessa ja Porvoossa ikäryhmittäin.svg")

p <- ggplot(trim(amount[amount$Area=="Finland",]), aes(x=Group, weight=amountResult, fill=Fish))+geom_bar()+
  coord_flip()+ facet_grid(Gender ~ .)+
  labs(
    title="Kalansyönti Suomessa ikäryhmittäin ja sukupuolittain",
    y="Syönti (g/d)"
  )
print(p)
ggsave("Kalansyönti Suomessa ikäryhmittäin.svg")


tmp <- oapply(amount[amount$Area!="Helsinki",],NULL,sum,"Fish")@output
p <- ggplot(tmp, aes(x=amountResult+1, colour=Group))+stat_ecdf()+
  scale_x_log10() + facet_grid(Area~.)+
  coord_cartesian(xlim=c(3,300))+
  labs(
    title="Kalansyönti väestössä",
    x="Kalansyönti (g päivässä)",
    y="Kumulatiivinen todennäköisyysjakauma"
  )

p
ggsave("Kalansyönnin jakauma Suomessa.svg")

ggplot(trim(EvalOutput(total_amount)), aes(x=Scenario, weight=total_amountResult, fill=Kala))+geom_bar()+
  labs(title="Kalan kokonaiskulutus Suomessa (milj kg /a)")

ggplot(conc_mehg@output, aes(x=conc_mehgResult, colour=Area))+stat_ecdf()+
  scale_x_log10()+facet_wrap(~Fish, scales="free_x")

ggplot(conc@output[conc$Compound %in% c("PFAS","PFOS"),], aes(x=concResult, color=Compound, linetype=Area))+stat_ecdf()+
  scale_x_log10()+
#  stat_ecdf(data=conc_eukalat@output, aes(x=conc_eukalatResult))+
  scale_linetype_manual(values=c("dotted","twodash","solid"))+
  labs(
    title="PFAS-pitoisuudet kalassa Suomessa",
    x="PFAS-pitoisuus (ng/g tuorepainoa)",
    y="Kumulatiivinen todennäköisyys"
  )
# The code may produce some negative values, which are removed from the graph
ggsave("PFAS-pitoisuus kalassa Suomessa.svg")

ggplot(conc@output, aes(x=concResult, colour=Fish))+stat_ecdf()+
  facet_wrap(~Compound, scales="free_x")+scale_x_log10()

limits <- data.frame(
  Exposure_agent = c("TEQ","MeHg","PFAS","Vitamin D","Fish"),
  Type = c("TDI","TDI","TDI","RDI","RDI"),
  Result = c(2*70/7, 1.3*70/7,4.4*70/7,10,200/7)
)

tmp <- EvalOutput(expo_dir, verbose=TRUE) # Calculated again because we want Group, which is collapsed
tmp <- oapply(tmp,NULL,sum, c("Fish","fish_proportionSource","amountSource","concSource"))
tmp <- oapply(tmp,NULL,mean,"Scaling") # Not all scales are available for all Exposure agents, but all are identical
tmp <- tmp[tmp$Exposcen=="BAU" & !tmp$Exposure_agent %in% c("ALA", "EPA") , ]
tmp$Group <- factor(tmp$Group, levels=c("Toddlers","Other children","Adolescents","Adults","Elderly"))

tmp2 <- tmp[tmp$Exposure_agent=="PFAS",] 
limits2 <- limits[limits$Exposure_agent=="PFAS",]
ggplot(la(tmp2@output), aes(x=expo_dirResult+0.5, colour=Ryhmä))+stat_ecdf()+
  scale_x_log10()+ facet_grid(Alue ~ .)+
  geom_vline(data=la(limits2), aes(xintercept=Result, linetype=Päiväsaanti))+
  geom_point(data = la(oapply(tmp2,c("Group","Exposure_agent","Area"),mean)@output),
             aes(x=expo_dirResult, y=0.1), shape=1, size=3, stroke=2)+
  thlTheme(legend.position = "right")+
  labs(title="PFAS-yhdisteiden saanti kalasta
       eri ryhmissä",
       subtitle="Suora altistuminen päivässä (ng/pvä)",
       y="todennäköisyys"
  )

ggsave("PFAS-yhdisteiden saanti kalasta Suomessa ja Porvoossa.svg")

tmp <- tmp[tmp$Area=="Finland",]
ggplot(la(tmp@output), aes(x=expo_dirResult+0.5, colour=Ryhmä))+stat_ecdf()+
  scale_x_log10() + facet_wrap(~Altiste, scales="free_x", ncol=2)+
  geom_vline(data=la(limits), aes(xintercept=Result, linetype=Päiväsaanti))+
  geom_point(data = la(oapply(tmp,c("Group","Exposure_agent"),mean)@output),
             aes(x=expo_dirResult, y=0.1), shape=1, size=3, stroke=2)+
  thlTheme(legend.position = "right")+
  labs(title="Yhdisteiden saanti kalasta",
       subset="Suora altistuminen päivässä (kala: g, rasvahapot: mg, D-vit: ug, PFAS: ng, TEQ: pg)",
       y="todennäköisyys")

ggsave("Yhdisteiden saanti kalasta Suomessa.svg", width=7, height=10)

ggplot(trim(tmp), 
       aes(x=Age, weight=expo_dirResult, fill=Gender))+geom_bar(position="dodge")+
  facet_wrap(~Exposure_agent, scales="free_y")+
  scale_x_discrete(breaks = levels(ages)[seq(1,length(ages),4)])+
  labs(
    title="Suora altistuminen yhdisteille",
    y="(omega mg/d. vit D ug/d. PFAS ng/d)"
  )

ggplot(expo_indir@output[expo_indir$Exposcen=="BAU",],
       aes(x=expo_indirResult+0.03,color=Area,linetype=Age))+
  stat_ecdf()+scale_x_log10()+facet_wrap(~Exposure_agent)+
  labs(title="Epäsuora altistuminen äidistä lapseen",
       y="Kumulatiivinen todennäköisyysjakauma",
       x="(DHA mg/d [ä]iti, TEQ pg/g rasva [l]apsi, PFAS ng/ml veri [l], MeHg ug/g hius [ä])")
ggsave("Epäsuora altistuminen äidistä lapseen.svg")

cat("Kalaperäisiä tautitaakkoja Suomessa\n")

if(openv$N>1) {
  tmp <- summary(ERF)
  tmp <- data.frame(
    Altiste = tmp$Exposure_agent,
    Vaikutus = tmp$Response,
    Annosvastefunktio = tmp$ER_function,
    Skaalaus = tmp$Scaling,
    Havainto = tmp$Observation,
    Keskiarvo = as.character(signif(tmp$mean,2)),
    "95 luottamusväli" = paste0(signif(tmp$Q0.025,2)," - ", signif(tmp$Q0.975,2)),
    Keskihajonta = signif(tmp$sd,2)
  )#[rev(match(lev, tmp$Exposure_agent)),]

  oprint(tmp)
  
  tmp2 <- summary(oapply(BoDattr[BoDattr$Area=="Finland",],NULL,sum,c("Age","Gender","Exposure_agent","Response")))
  tmp2 <- data.frame(
    Alue = tmp2$Area,
    Keskiarvo = signif(tmp2$mean,2),
    "95 luottamusväli" = paste0(signif(tmp2$Q0.025,2)," - ", signif(tmp2$Q0.975,2)),
    Keskihajonta = signif(tmp2$sd,2)
  )

  tmp <- summary(oapply(BoDattr[BoDattr$Area=="Finland",],NULL,sum,c("Age","Gender")))
  tmp <- orbind(data.frame(
    Altiste = tmp$Exposure_agent,
    Vaste = tmp$Response,
#    Alue = tmp$Area,
    Keskiarvo = as.character(signif(tmp$mean,2)),
    "95 luottamusväli" = paste0(signif(tmp$Q0.025,2)," - ", signif(tmp$Q0.975,2)),
    Keskihajonta = signif(tmp$sd,2)
  ),
  data.frame(Altiste="Yhteensä", tmp2[-6])) # remove Alue

  oprint(la(tmp))
  
  tmp <- summary(oapply(BoDattr[BoDattr$Area=="Finland",],NULL,sum,c("Age","Gender","Response")))
  tmp <- orbind(data.frame(
    Altiste = tmp$Exposure_agent,
    Alue = tmp$Area,
    Keskiarvo = as.character(signif(tmp$mean,2)),
    "95 luottamusväli" = paste0(signif(tmp$Q0.025,2)," - ", signif(tmp$Q0.975,2)),
    Keskihajonta = signif(tmp$sd,2)
  ),
  data.frame(Altiste="Yhteensä", tmp2))

  oprint(tmp)
  
  tmp <- summary(oapply(BoDattr[BoDattr$Area=="Finland",],NULL,sum,c("Age","Gender","Exposure_agent")))
  tmp <- orbind(data.frame(
    Terveysvaikutus = tmp$Response,
    Alue = tmp$Area,
    Keskiarvo = signif(tmp$mean,2),
    "95 luottamusväli" = paste0(signif(tmp$Q0.025,2)," - ", signif(tmp$Q0.975,2)),
    Keskihajonta = signif(tmp$sd,2)
  ),
  data.frame(Terveysvaikutus="Yhteensä", tmp2))

  oprint((tmp))
}

tmp <- trim(BoDattr[BoDattr$Area=="Finland",])
ggplot(tmp, aes(x=Exposure_agent, weight=BoDattrResult, fill=Response),colour="black")+geom_bar()+
  labs(
    title="Tautitaakka kalasta tekijöittäin",
    x="Kalassa oleva tekijä",
    y="Tautitaakka (DALY/a)"
  )
ggsave("Tautitaakka kalasta tekijöittäin.svg")

tmp2 <- trim(oapply(BoDattr,c("Area","Age","Iter"),sum))
tmp2 <- tmp2[tmp2$Area=="Finland",]
ggplot(tmp2, aes(x=Age, y=-BoDattrResult, group=Area))+geom_line(size=2,colour="#48c232")+
  scale_x_discrete(breaks = levels(ages)[seq(1,length(ages),4)])+
  thlTheme()+
  labs(
    title="Terveyshyöty kalasta ikäryhmittäin",
    x="Ikäryhmä",
    subtitle="Terveystyöty (-DALY/a)",
    y=""
  )
ggsave("Terveyshyöty kalasta ikäryhmittäin.svg")

ggplot(tmp[tmp$Age=="0 - 4" & tmp$Gender=="Male" , ], 
       aes(x=Exposure_agent, weight=BoDattrResult, fill=Response),color="black")+geom_bar()+
  labs(
    title="Tautitaakka kalasta tekijöittäin pikkupojilla",
    x="Kalassa oleva tekijä",
    y="Tautitaakka (DALY/a"
  )
ggsave("Tautitaakka kalasta tekijöittäin pikkupojilla Suomessa.svg")

tmp <- trim(BoDattr)
ggplot(tmp[tmp$Age=="0 - 4" & tmp$Gender=="Male" & tmp$Area!="Helsinki" , ], 
       aes(x=Exposure_agent, weight=BoDattrResult, fill=Response),color="black")+geom_bar()+
  facet_wrap(~ Area)+
  labs(
    title="Tautitaakka kalasta tekijöittäin pikkupojilla",
    x="Kalassa oleva tekijä",
    y="Tautitaakka (DALY/a"
  )
ggsave("Tautitaakka kalasta tekijöittäin pikkupojilla.svg")

ggplot(tmp, aes(x=Age, weight=BoDattrResult, fill=Response))+geom_bar(position="stack")+
  scale_x_discrete(breaks = levels(ages)[seq(1,length(ages),4)])+
  labs(
    title="Tautitaakka kalassa olevista tekijöistä",
    x="Ikäryhmä",
    y="Tautitaakka (DALY/a)"
  )
ggsave("Tautitaakka kalassa olevista tekijöistä.svg")

tmp <- trim(oapply(BoDattr[BoDattr$Area=="Finland",],c("Response","Exposure_agent","Iter"),sum))
tmp$r <- sqrt(abs(tmp$BoDattrResult))
tmp$x0 <- c(-100, 100, 100, 100, 100,-200,-500,-100,-250,-100, 100)
tmp$y0 <- c(-180,-120, -60,   0,  60, 170, 100,  50,-100, 250, 120)
tmp <- rbind(tmp,data.frame(
  Response = c("Hyödyt","Haitat"),
  Exposure_agent= c("TEQ","TEQ"),
  BoDattrResult=c(0,0),
  r=c(0,0),
  x0=c(-250,100),
  y0=c(350,350)
))
ggplot(la(tmp), aes(x0=x0, y0=y0, r=r, fill=Altiste))+geom_circle(aes(color=Altiste))+
  geom_text(aes(x=x0, y=y0, label=Vaikutus), hjust=-0.1)+
  coord_cartesian(xlim=c(-750, 400))+
  thlTheme(
    legend.position ="bottom",
    show.grid.y=FALSE)+
  theme(
    axis.title=element_blank(),
    axis.text=element_blank(),
    axis.ticks=element_blank())+
  labs(
    title="Tautitaakka kalan eri tekijöistä",
    y=""
  )

ggsave("Suomen tautitaakka kalasta pallokuviona.svg", height=5, width = 9)

tmp <- BoDattr / population * 1000

p <- ggplot(trim(tmp[tmp$Area!="Helsinki",]), aes(x=Age, weight=Result, fill=Response))+geom_bar(position="stack")+
  scale_x_discrete(breaks = levels(ages)[seq(1,length(ages),4)])+
  labs(
    title="Tautitaakka kalassa olevista tekijöistä per henkilö",
    x="Ikäryhmä",
    y="Tautitaakka (mDALY/hlö/a)"
  ) + facet_wrap(~Area)
  oprint(p)
  ggsave("Tautitaakka kalassa olevista tekijöistä per henkilö.svg")
  
  ggplot(trim(PAF), aes(x=PAFResult, colour=Response))+stat_ecdf()


tmp <- expo_dir + Ovariable("limits", data=limits)
tmp <- tmp[!(tmp$Exposure_agent=="TEQ"&tmp$Scaling=="BW") & tmp$Exposcen=="BAU",]
tmp <- tmp[tmp$Area=="Finland",]
tmp$tst <- paste(tmp$Iter, tmp$Gender, tmp$Age)
#tst <- CollapseMarginal(tmp,"Age",fun="sample",
#  probs=list(Age=result(oapply(population[population$Age!="Undefined",],"Age",sum))))

# This Venn diagram produced the following numbers for the different subgroups
# no-RDI, no-TWI: 4184
# RDI only: 99
# TDI only: 1666
# Both RDI+TDI: 1251
# Total: 7200 (200 iterations, 2 Genders, 18 ages) # Actually Age should be collapsed, weighted by population. 
# Not critical in Finland because so similar age group sizes. Besides reduces number of observations,
# and should be rerun with more iterations.
# the ovariable has 36000 rows: (in addition 5 Exposure_agents)
if(FALSE) {
ggVennDiagram(list(
  All = tmp$tst[tmp$Exposure_agent=="TEQ"],
#  MeHg = tmp$tst[tmp$Exposure_agent=="MeHg" & tmp$expo_dirResult > tmp$limitsResult],
#  TEQ = tmp$tst[tmp$Exposure_agent=="TEQ" & tmp$expo_dirResult > tmp$limitsResult],
#  PFAS = tmp$tst[tmp$Exposure_agent=="PFAS" & tmp$expo_dirResult > tmp$limitsResult],
#  VitD = tmp$tst[tmp$Exposure_agent=="Vitamin D" & tmp$expo_dirResult > tmp$limitsResult]
  RDI = tmp$tst[tmp$Type=="RDI" & tmp$expo_dirResult > tmp$limitsResult],
  TDI = tmp$tst[tmp$Type=="TDI" & tmp$expo_dirResult > tmp$limitsResult]
))
}
################ Insight network
#gr <- scrape(type="assessment")
#objects.latest("Op_en3861", "makeGraph") # [[Insight network]]
#gr <- makeGraph(gr)
#export_graph(gr, "ruori.svg")
#render_graph(gr) # Does not work: Error in generate_dot(graph) : object 'attribute' not found
##################### Diagnostics
#objects.latest("Op_en6007", code_name="diagnostics")
#print(showLoctable())
#print(showind())

# Self-made Venn diagram
# Take two circles: 
# first is the unit circle x^2 + y^2 = 1
# second circle has centre at x-axis: (x-a)^2 + y^2 = r^2, r <= 1, 0 <= a <= r+1
# In other words, the other circle is never bigger and left to the first circle.
# This leads to a situation where the intercept always starts from (a-r,0) and goes to (min(1,a+r),0).

# Solve for the upper intercept point by replacing y^2:
# x^2 - 2ax + a^2 + (1 - x^2) = r^2
# x = (a^2 + 1 - r^2) / 2a

intercept <- function(a, r) {
  x <- (a^2 + 1 - r^2) / (2*a)
  y <- sqrt(1 - x^2)
  cat("intercept",x,y,"\n")
  return(c(x,y))
}

# Area of a segment of the unit circle integral sqrt(1 - x^2) dx = 1/2(sqrt(1-x^2)x+sin^-1(x))

# Area of segment of the other circle y = sqrt(r^2 - (x-a)^2)
# 1/2*((x-a)*sqrt(-a^2 + 2*a*x + r^2 - x^2) + r^2 * atan((x-a)/sqrt(r^2 - (a-x)^2)))

area <- function(a0, r0) {

  integ <- function(x, a, r) {
    out <- 1/2*((x-a)*sqrt(max(0,-a^2 + 2*a*x + r^2 - x^2)) + r^2 * atan((x-a)/sqrt(r^2 - (a-x)^2)))
    cat("integ",out,"\n")
    return(out)
  }
  A1 <- integ(intercept(a0,r0)[1], a0, r0) - integ(a0-r0, a0, r0) # left segment by the second circle
  A2 <- integ(min(1,a0+r0), 0, 1) - integ(intercept(a0,r0)[1], 0, 1) # right segment by the unit circle
  return(2*(A2 + A1)/pi) # returns the intercept area relative to unit circle
}
area(0.38,sqrt(1251/(1251+1666)))
1251/(1251+1666)
df <- data.frame(
  x0=c(0,0.384,0.1),
  r=sqrt(c(1,(1251+99)/(1251+1666),(99+1251+1666+4184)/(1251+1666))),
  y0=c(0,0,0),
  Ryhmä=c("TDI ylittyy","RDI saavutetaan","Koko väestö")
)
ggplot(data=df, aes(x0=x0, y0=y0,r=r, fill=Ryhmä))+geom_circle(alpha=0.3)+
  theme(
    axis.title=element_blank(),
    axis.text=element_blank(),
    axis.ticks=element_blank())+
  thlTheme(
    legend.position ="bottom",
    show.grid.y = FALSE)+
  labs(
    title="Suomalaisten sijoittuminen päiväsaantien suhteen",
    y=""
  )

ggsave("Venn_raja_arvoylitykset_kala_altistumisessa.svg", width=7, height=6)

```

```{r finale}
# Run all above
```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
