---
title: "Fish and health in Finland and Porvoo: results with special focus on PFAS compounds"
author: "Jouni Tuomisto"
date: "07 03 2021"
output: html_document
params:
  N: 200
  porvoo: FALSE
---
## Shortcut to model download

This is an open assessment looking at health effects of fish consumption in Finland. The details of the assessment are described at [Opasnet](http://fi.opasnet.org/fi/PFAS-yhdisteiden tautitaakka). This file contains the R code to run the assessment model.

This code downloads all the ovariables created by the previous code, fishhealth_initiate.Rmd, runs the model and plots various graphs and tables about the results.

Fix these problems:

2. Calculate total personal BoD for individuals in Porvoo and Helsinki. Do not compare those at the (Finnish) population level. DONE
3. Correct the fish intake distribution to manage dimension Area correctly. DONE
4. Check that all oapply NA-fillings are intended. DONE
5. Correct the "Kalansyönti Suomessa keskimäärin" figure. DONE
6. PFOS, PFAS: ug/g --> ng/g DONE
7. PFAS: separate Porvoo from other regions. DONE
8. NOTE! Salmon concentrations include farmed salmon at the moment. This is OK for health impact assessment. DONE
9. Is amount / Group good for fillna? check. Solution: Yes, because Inpamount does not contain Group. DONE
10. Is expo_locations still used? Yes. DONE 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) 

library(OpasnetUtils) # Install the newest version from https://github.com/jtuomist/OpasnetUtils not from CRAN.
library(tidyverse)
library(plotly)
library(readxl)
library(reshape2)

openv.setN(params$N)

```


```{r modelrun}

objects.latest("Op_fi5932",code_name="initiate") # [[PFAS-yhdisteiden tautitaakka]]

conc_eukalat <- EvalOutput(conc_eukalat)
BoDattr <- EvalOutput(BoDattr, verbose=TRUE)

```

```{r summary tables}

oprint(summary(amount,"mean"))
oprint(summary(BoD,marginals=c("Age","Response"),"mean"))
oprint(summary(BoD,marginals=c("Gender","Response"),"mean"))
oprint(summary(BoDattr,marginals=c("Age","Response"),"mean"))
oprint(summary(BoDattr,marginals=c("Exposure_agent","Response"),"mean"))
oprint(summary(BoDattr,marginals=c("Gender","Response"),"mean"))
oprint(summary(case_burden,"mean"))
oprint(summary(conc,"mean"))
oprint(summary(dose,"mean"))
oprint(summary(ERF,"mean"))
oprint(summary(expo_dir,"mean"))
oprint(summary(expo_dir,marginals="Exposure_agent"))
oprint(summary(expo_indir,"mean"))
oprint(summary(exposure,"mean"))
#oprint(summary(fish_proportion,"mean"))
oprint(summary(incidence,"mean"))
oprint(summary(PAF,"mean"))
oprint(summary(population,"mean"))
oprint(summary(RR,"mean"))


```


```{r plots}
###################
# Graphs
tmp <- trim(amount)
tmp <- tmp[tmp$Area!="Helsinki",]
tmp$Group <- factor(tmp$Group, levels=c("Infants","Toddlers","Other children","Adolescents",
                                        "Adults", "Elderly"))

if(params$porvoo) {
  p <- ggplot(tmp, aes(x=Group, weight=amountResult, fill=Fish))+geom_bar()+
    coord_flip()+ facet_grid(Area ~ Gender)+
    labs(
      title="Kalansyönti Suomessa ja Porvoon vapaa-ajankalastajilla ikäryhmittäin",
      y="Syönti (g/d)"
    )
  print(p)
  ggsave("Kalansyönti Suomessa ja Porvoossa ikäryhmittäin.svg")
} else {
  p <- ggplot(tmp[tmp$Area=="Finland",], aes(x=Group, weight=amountResult, fill=Fish))+geom_bar()+
    coord_flip()+ facet_grid(Gender ~ .)+
    labs(
      title="Kalansyönti Suomessa ikäryhmittäin ja sukupuolittain",
      y="Syönti (g/d)"
    )
  print(p)
  ggsave("Kalansyönti Suomessa ikäryhmittäin.svg")
}

tmp <- oapply(amount[amount$Area!="Helsinki",],NULL,sum,"Fish")@output
p <- ggplot(tmp, aes(x=amountResult+1, colour=Group))+stat_ecdf()+
  scale_x_log10() + facet_grid(Area~.)+
  coord_cartesian(xlim=c(3,300))+
  labs(
    title="Kalansyönti väestössä",
    x="Kalansyönti (g päivässä)",
    y="Kumulatiivinen todennäköisyysjakauma"
  )

p
ggsave("Kalansyönnin jakauma Suomessa.svg")

ggplot(trim(EvalOutput(total_amount)), aes(x=Scenario, weight=total_amountResult, fill=Kala))+geom_bar()+
  labs(title="Kalan kokonaiskulutus Suomessa (milj kg /a)")

ggplot(conc_mehg@output, aes(x=conc_mehgResult, colour=Area))+stat_ecdf()+
  scale_x_log10()+facet_wrap(~Fish, scales="free_x")

ggplot(conc@output[conc$Compound %in% c("PFAS","PFOS"),], aes(x=concResult, color=Compound, linetype=Area))+stat_ecdf()+
  scale_x_log10()+
#  stat_ecdf(data=conc_eukalat@output, aes(x=conc_eukalatResult))+
  scale_linetype_manual(values=c("dotted","twodash","solid"))+
  labs(
    title="PFAS concentration in fish in Finland",
    x="PFAS concentration (ng/g fresh weight)",
    y="Cumulative probability"
  )
# The code may produce some negative values, which are removed from the graph
ggsave("PFAS-pitoisuus kalassa Suomessa.svg")

ggplot(conc@output, aes(x=concResult, colour=Fish))+stat_ecdf()+
  facet_wrap(~Compound, scales="free_x")+scale_x_log10()

limits <- data.frame(
  Exposure_agent = c("TEQ","MeHg","PFAS","Vitamin D"),
  Type = c("TDI","TDI","TDI","RDI"),
  Result = c(2*70/7, 1.3*70/7,4.4*70/7,10)
)

tmp <- EvalOutput(expo_dir, verbose=TRUE) # Calculated again because we want Group, which is collapsed
tmp <- oapply(tmp,NULL,sum,c("Fish","fish_proportionSource","amountSource","concSource"))
tmp <- oapply(tmp,NULL,mean,"Scaling")
tmp <- tmp[tmp$Exposcen=="BAU" & !tmp$Exposure_agent %in% c("ALA", "EPA") ,]
tmp$Group <- factor(tmp$Group, levels=c("Toddlers","Other children","Adolescents","Adults","Elderly"))
if(params$porvoo) {
  tmp <- tmp[tmp$Exposure_agent=="PFAS",] 
  limits <- limits[limits$Exposure_agent=="PFAS",]
  titl <- "PFAS-yhdisteiden saanti kalasta eri ryhmissä"
} else titl <- "Yhdisteiden saanti kalasta"
p <- ggplot(tmp@output[tmp$Area=="Finland",], aes(x=expo_dirResult+0.5, colour=Group))+stat_ecdf()+
  scale_x_log10()+
  geom_vline(data=limits, aes(xintercept=Result, linetype=Type))+
  geom_point(data = oapply(tmp,c("Group","Exposure_agent","Area"),mean)@output,
             aes(x=expo_dirResult, y=0.1), shape=1, size=3, stroke=2)+
  labs(title=titl,
       x="Suora altistuminen päivässä (kala: g, rasvahapot: mg, D-vit: ug, PFAS: ng, TEQ: pg)",
       y="kumulatiivinen todennäköisyys")
if(params$porvoo) {
  p <- p + facet_grid(Area ~ .)
  print(p)
  ggsave("PFAS-yhdisteiden saanti kalasta Suomessa ja Porvoossa.svg")
} else {
  p <- p + facet_wrap(~Exposure_agent, scales="free_x")
  print(p)
  ggsave("Yhdisteiden saanti kalasta Suomessa.svg")
}

ggplot(trim(tmp[tmp$Area=="Finland",]), 
       aes(x=Age, weight=expo_dirResult, fill=Gender))+geom_bar(position="dodge")+
  facet_wrap(~Exposure_agent, scales="free_y")+
  labs(
    title="Exposure to compounds",
    y="(omega: mg/d; vit D: ug/d, PFAS: ng/d)"
  )

cat("Kalaperäisiä tautitaakkoja Suomessa\n")

if(openv$N>1) {
  tmp <- summary(ERF)
  tmp <- data.frame(
    Altiste = tmp$Exposure_agent,
    Vaikutus = tmp$Response,
    Annosvastefunktio = tmp$ER_function,
    Skaalaus = tmp$Scaling,
    Havainto = tmp$Observation,
    Keskiarvo = as.character(signif(tmp$mean,2)),
    "95 luottamusväli" = paste0(signif(tmp$Q0.025,2)," - ", signif(tmp$Q0.975,2)),
    Keskihajonta = signif(tmp$sd,2)
  )#[rev(match(lev, tmp$Exposure_agent)),]

  oprint(tmp)
  
  tmp <- summary(oapply(BoDattr[BoDattr$Area=="Finland",],NULL,sum,c("Age","Gender","Response")))
  tmp <- data.frame(
    Altiste = tmp$Exposure_agent,
    Alue = tmp$Area,
    Keskiarvo = as.character(signif(tmp$mean,2)),
    "95 luottamusväli" = paste0(signif(tmp$Q0.025,2)," - ", signif(tmp$Q0.975,2)),
    Keskihajonta = signif(tmp$sd,2)
  )#[rev(match(lev, tmp$Exposure_agent)),]

  oprint(tmp)
  
  tmp <- summary(oapply(BoDattr[BoDattr$Area=="Finland",],NULL,sum,c("Age","Gender","Exposure_agent")))
  tmp <- data.frame(
    Terveysvaikutus = tmp$Response,
    Alue = tmp$Area,
    Keskiarvo = signif(tmp$mean,2),
    "95 luottamusväli" = paste0(signif(tmp$Q0.025,2)," - ", signif(tmp$Q0.975,2)),
    Keskihajonta = signif(tmp$sd,2)
  )
  oprint(tmp)

  tmp2 <- summary(oapply(BoDattr[BoDattr$Area=="Finland",],NULL,sum,c("Age","Gender","Exposure_agent","Response")))
  tmp2 <- data.frame(
    Terveysvaikutus = "Yhteensä",
    Alue = tmp2$Area,
    Keskiarvo = signif(tmp2$mean,2),
    "95 luottamusväli" = paste0(signif(tmp2$Q0.025,2)," - ", signif(tmp2$Q0.975,2)),
    Keskihajonta = signif(tmp2$sd,2)
  )
  oprint(tmp2)
}

tmp <- trim(BoDattr[BoDattr$Area=="Finland",])
ggplot(tmp, aes(x=Exposure_agent, weight=BoDattrResult, fill=Response),colour="black")+geom_bar()+
  labs(
    title="Tautitaakka kalasta tekijöittäin",
    x="Kalassa oleva tekijä",
    y="Tautitaakka (DALY/a"
  )
ggsave("Tautitaakka kalasta tekijöittäin.svg")

ggplot(tmp[tmp$Age=="0 - 4" & tmp$Gender=="Male",], 
       aes(x=Exposure_agent, weight=BoDattrResult, fill=Response),color="black")+geom_bar()+
  labs(
    title="Tautitaakka kalasta tekijöittäin pikkupojilla",
    x="Kalassa oleva tekijä",
    y="Tautitaakka (DALY/a"
  )
ggsave("Tautitaakka kalasta tekijöittäin pikkupojilla.svg")

ggplot(tmp, aes(x=Age, weight=BoDattrResult, fill=Response))+geom_bar(position="stack")+
  scale_x_discrete(breaks = levels(ages)[seq(1,length(ages),3)])+
  labs(
    title="Tautitaakka kalassa olevista tekijöistä",
    x="Ikäryhmä",
    y="Tautitaakka (DALY/a)"
  )
ggsave("Tautitaakka kalassa olevista tekijöistä.svg")

tmp <- BoDattr / population * 1000

p <- ggplot(trim(tmp[tmp$Area!="Helsinki",]), aes(x=Age, weight=Result, fill=Response))+geom_bar(position="stack")+
  scale_x_discrete(breaks = levels(ages)[seq(1,length(ages),3)])+
  labs(
    title="Tautitaakka kalassa olevista tekijöistä per henkilö",
    x="Ikäryhmä",
    y="Tautitaakka (mDALY/hlö/a)"
  ) + facet_wrap(~Area)
  oprint(p)
  ggsave("Tautitaakka kalassa olevista tekijöistä per henkilö.svg")

################ Insight network
#gr <- scrape(type="assessment")
#objects.latest("Op_en3861", "makeGraph") # [[Insight network]]
#gr <- makeGraph(gr)
#export_graph(gr, "ruori.svg")
#render_graph(gr) # Does not work: Error in generate_dot(graph) : object 'attribute' not found
##################### Diagnostics
#objects.latest("Op_en6007", code_name="diagnostics")
#print(showLoctable())
#print(showind())

```

```{r finale}
# Run all above
```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
