---
title: "Fish and health with national fish promotion programme"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

This is an open assessment looking at potential health effects of a national fish promotion program in Finland. The details of the assessment are described at [Opasnet](http://fi.opasnet.org/fi/PFAS-yhdisteiden tautitaakka). This file contains the R code to run the assessment model.

Knit to html for best performance.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) 

library(OpasnetUtils) # Install the newest version from https://github.com/jtuomist/OpasnetUtils not from CRAN.
library(tidyverse)
library(plotly)

# First empty all objects for a fresh start. Otherwise may be problems with CheckDecisions.
oempty(all=TRUE)
openv.setN(0)

objects.latest("Op_en2031", code_name="subgrouping") # [[Exposure-response function]] subgrouping

#' prepare adjusts the data table for ovariables. Requires function subgrouping from code Op_en2031/subgrouping on page [[Exposure-response function]]
#' @param dat data.frame
#' @param type type of data that is used. Must match content in column Type
#' @param drop columns to remove
#' @return data.frame
prepare <- function(dat, type=NULL, drop=NULL) {
  out <- dat
  if(!is.null(type)) out <- out[out$Type %in% type , ]
  if(!is.null(drop)) out <- out[!colnames(out) %in% drop]
  return(subgrouping(out))
}

#' Copies results from one location to other locations while keeping everything else constant
#' @param ova ovariable to be used
#' @param locations list of relevant indices. Each item is a list that has a name of an existing locations, and the content is a vector of new location names.
#' @return the input ovariable with new rows containing the new locations

expand_index <- function(ova, locations) {
  if("ovariable" %in% class(ova)) out <- ova@output else out <- ova
  for(i in names(locations)) {
    for(j in names(locations[[i]])) {
      addpiece <- out[out[[i]]==j,]
      for(k in locations[[i]][[j]]) {
        addpiece[[i]] <- k
        out <- rbind(out,addpiece)
      }
    }
  }
  if("ovariable" %in% class(ova)) ova@output <- out else ova <- out
  return(ova)
}

```

Calculation is based on BONUS GOHERR project and its [fish health benefit-risk assessment](http://en.opasnet.org/w/Goherr_assessment).

What needs to be done for PFAS assessment?

1. Amount should be gender and age-specific, because we need to worry about young mothers. Solution: take KKE amounts of fish, and scale those with the Goherr subgroup-specific proportions. DONE. Not age-specific atm.
2. Amounts should reflect the actual fish consumption in Porvoo. Solution: postpone and use national statistics. DONE
3. Infant's dioxin concentration module must be added. Solution: Use Goherr model for expo_indir DONE
4. The module must be updated to match PFAS as well. Solution: update the module to contain column Exposure_agent. Change body fat parameter to volume of distribution. DONE but not checked. 
5. Find why expo_indir is so much higher than EFSA toxicokinetic assessment. Make an alternative model.
6. Add ERF for PFAS (sum of PFOS, PFHxS, PFOA, PFNA). Solution: Make a new page for ERF of PFAS and add that to adjusted ERFs. First immunology; postpone cholesterol and low birth weight and liver toxicity. DONE
7. Add case burdens for PFAS outcomes. Solution: give rough estimates for immunology to get started. DONE
8. Add PFAS concentrations to data. Solution: Look at Porvoo concentrations first and make conc_pfas; combine that with conc_vit. DONE
9. Add dioxin and MeHg concentrations. DONE
10. Now that the model runs technically, look through each part to check that it makes sense.
11. If PAF contains some inputs with Age and some without Age (implying that they apply to any age group), only the explicit age groups remain in the end. Solution: Add RRorig to compensate for this. DONE
12. TEQ and MeHg are missing from dose. Check why and correct. DONE
13. The proportions of All-cause mortality and CHD2 mortality are 3:1 in [Kotimaisen kalan edistämisohjelma](http://fi.opasnet.org/fi/Kotimaisen_kalan_edist%C3%A4misohjelma) but 3:2 in this analysis. Why?
14. In exposure, ALA + DHA < Omega3. Why?
15. BoDattr: age group 45 - 50 is way smaller than any other group. Why?
16. conc_mehg does not contain Iter although it is probabilistic. Solution: Update formula. DONE
17. All TEQ responses are way too large. Why? Is there a unit problem?
18. MeHg exposure is ca. 2 ug/d when you would assume 1 mg/kg * 0.03 kg/d = 30 ug/d. Where is the difference?

```{r case-specific adjustments}

objects.latest("Op_en2261", code_name="RR2") # RR on page [[Health impact assessment]]

RRorig <- RR@formula

RR@formula <- function(...) {
  out <- RRorig()
  out <- out * Ovariable(output=data.frame(Age=c(
    "0 - 4", "5 - 9", "10 - 14", "15 - 19", "20 - 24", "25 - 29", "30 - 34", "35 - 39", "40 - 44", "45 - 49", "50 - 54",
    "55 - 59", "60 - 64", "65 - 69", "70 - 74", "75 - 79", "80 - 84", "85+", "Undefined"),
    Result=1),
    marginal=c(TRUE,FALSE)
  )
  return(out)
}

```

```{r downloads}
# This code was forked from https://github.com/jtuomist/fishhealth/blob/master/fishhealth.Rmd
# This code was previously forked from code Op_fi5923/model on page [[Kotimaisen kalan edistämisohjelma]]
# The code was even more previously forked from Op_fi5889/model on page [[Ruori]] and Op_en7748/model on page [[Goherr assessment]]

dat <- opbase.data("Op_fi5932", subset="Malliparametrit")[-1] # [[PFAS-yhdeisteiden tautitaakka]]
dec <- opbase.data("Op_fi5932", subset="Decisions")[-1]
DecisionTableParser(dec)

CTable <- opbase.data("Op_fi5932",subset="CollapseMarginals")
#for(i in 1:ncol(CTable)) {CTable[[i]] <- as.character(CTable[[i]])} # The default is currently character, not factor
CollapseTableParser(CTable)

cat("Laskennassa käytetty data.\n")
dat
cat("Tarkastellut päätökset.\n")
dec
cat("Aggregoidut marginaalit.\n")
CTable

dummy <- Ovariable("dummy",data=data.frame(Age="dummy", Fish="dummy", Compound="dummy", Area="dummy", Result=1)) # Keep these columns marginals

fish_proportion <- Ovariable( # How population subgroups eat fish differently
  "fish_proportion",
  data = data.frame(prepare(dat,"fish proportion",c("Type","Exposure_agent","Response","Unit"))),
  unit="proportion of the mean")

total_amount <- Ovariable(
  "total_amount",
  data=prepare(dat, "amount", c("Type","Response","Exposure_agent","Unit")),
  unit="M kg/a")

amount <- Ovariable(
  "amount",
  dependencies = data.frame(Name=c("total_amount", "fish_proportion")),
  formula = function(...) {
    amount <- total_amount
      # Filleted weight, i.e. no loss.
    amount <- amount * 1000 / 5.52 /365.25 
      # M kg/a per 5.52M population --> g/d per average person.
    amount <- amount * fish_proportion
      # fish_proportion tells the relative amount in each subgroup
  
    # Match KKE-classification in amount with Fineli classification
    tmp <- Ovariable(
      output = data.frame(
        Kala = c("Kasvatettu", "Kaupallinen", "Kirjolohi", "Silakka", "Vapaa-ajan", "Muu tuonti", "Tuontikirjolohi", "Tuontilohi"),
        Fish = c("Whitefish", "Average fish","Rainbow trout", "Herring", "Average fish", "Average fish", "Rainbow trout", "Salmon"),
        Result = 1
      ),
      marginal = c(TRUE, TRUE, FALSE)
    )
    
    amount <- amount * tmp
    
    return(amount)
  },
  unit="g/d"
)
# Exposure:To child and To eater not needed, because dioxins are not (yet) included

population <- Ovariable(
  "population", 
  data=prepare(dat, "population", c("Type", "Exposure_agent", "Response","Unit")),
  unit = "#"
)
population@data$Age <- factor(population@data$Age, levels=c(
  "0 - 4", "5 - 9", "10 - 14", "15 - 19", "20 - 24", "25 - 29", "30 - 34", "35 - 39", "40 - 44", "45 - 49", "50 - 54",
  "55 - 59", "60 - 64", "65 - 69", "70 - 74", "75 - 79", "80 - 84", "85+", "Undefined"))

incidence <- Ovariable(
  "incidence",
  data = prepare(dat,"incidence",c("Type","Exposure_agent","Unit")),
  unit="1/person-year")
#incidence@data$Age[is.na(incidence@data$Age)] <- ""

case_burden <- Ovariable(
  "case_burden",
  data = prepare(dat,"case burden",c("Type", "Exposure_agent","Unit")),
  unit="DALY/case")

ERFchoice <- Ovariable(
  "ERFchoice",
  data = 
    prepare(dat, "ERFchoice", c("Unit", "Type"))
)

InpBoD <- EvalOutput(Ovariable( # Evaluated because is not a dependency but an Input
  "InpBoD",
  data = prepare(dat, "BoD", c("Type","Exposure_agent","Unit")),
  unit="DALY/a"
))
InpBoD$Response[InpBoD$Response=="All causes"] <- "All-cause mortality"
InpBoD$Response[InpBoD$Response=="Depressive disorders"] <- "Depression"
InpBoD$Response[InpBoD$Response=="Neoplasms"] <- "Cancer morbidity"
InpBoD$Response[InpBoD$Response=="Respiratory infections and tuberculosis"] <- "Immunosuppression" # Infections of 0-9-year-olds are assumed to represent the background BoD of immunosuppressive effect of PFAS
InpBoD$Response[InpBoD$Response=="Cardiovascular diseases"] <- "CHD2 mortality"

```

```{r concentrations}

conc_vit <- Ovariable(
  "conc_vit",
  ddata = "Op_en1838", # [[Concentrations of beneficial nutrients in fish]]
  subset = "Fineli data for common fish species",
  unit="ALA mg/g, DHA mg/g, Fish g/g, Omega3 mg/g, Vitamin D µg/g f.w. after adjustment"
)
  df = conc_vit@data
  df$Nutrient[df$Nutrient=="D-vitamiini (µg)"] <- "Vitamin D"
  df$Nutrient[df$Nutrient=="rasvahapot n-3 moni-tyydyttymättömät (g)"] <- "Omega3"
  df$Nutrient[df$Nutrient=="rasvahappo 18:3 n-3 (alfalinoleenihappo) (mg)"] <- "ALA"
  df$Nutrient[df$Nutrient=="rasvahappo 22:6 n-3 (DHA) (mg)"] <- "DHA"
  df$Nutrient[df$Nutrient=="proteiini (g)"] <- "Fish"
  df$conc_vitResult[df$Nutrient=="Fish"] <- "1"
  df <- dropall(df[df$Nutrient %in% c("Vitamin D", "Omega3", "ALA", "DHA", "Fish") , ])
conc_vit@data <- df

######## Concentration of PFAS

# Data from EU-kalat3 (Finland excl Vanhankaupunginlahti): # pg/g fresh weight
#       POP     mean       sd      min   Q0.025   median   Q0.975      max
# 2.5% PFOS 2055.757 1404.045 305.0399 330.1365 1533.269 5029.697 5814.935

# Data from EU-kalat3 (Vanhankaupunginlahti, Helsinki) # ng/g f.w.
#      POP   mean       sd      min   Q0.025   median   Q0.975      max
#2.5% PFOS 14.428 11.94542 1.499441 1.607789 15.64988 35.32517 38.91994

conc_eukalat <- EvalOutput(Ovariable(
  "conc_eukalat",
  data = data.frame(
    Area = c("Suomi","Helsinki"),
    Compound="PFOS",
    Result=c("2.056 (3.301 - 5.030)", "14.428 (1.499 - 35.325)")),
  unit="ng/g fresh weight"
))

conc_pfas_raw <- Ovariable(
  "conc_pfas_raw",
  ddata="Op_fi5932",subset="PFAS concentrations",
  unit="ng/g f.w.")

conc_pfas <- Ovariable(
  "conc_pfas",
  dependencies = data.frame(Name="conc_pfas_raw"),
  formula = function(...) {
    out <- conc_pfas_raw
    out$Source <- NULL
    out$Area <- "Porvoo"
    out <- expand_index(out, list(Fish=list(Perch=c(
      "Average fish", "Pike","Rainbow trout","Roach", "Salmon", "Vendace", "Whitefish"))))
    out@marginal <- c(TRUE, TRUE, FALSE, TRUE, TRUE)
    return(out)
  },
  unit="ng/g fresh weight"
)

#sum_pfas <- oapply(conc_pfas, cols=c("Kala","Compound"), FUN=sum)
#tmp <- conc_pfas / sum_pfas
#summary(tmp, marginals="Compound")
#
## This tells that PFOS consists of 71 - 97 % of the four key PFAS, while PFOA, PFNA, and PFHxS consist of 
# 0 - 10 %, 2 - 18 %, and 0 - 9 %, respectively.
# Even if we included the next most abundant congeners, i.e. PFDA and PFUnA, the overall picture would not change.

conc <- Ovariable(
  "conc",
  dependencies = data.frame(
    Name=c("conc_vit", "conc_pfas","conc_pcddf","conc_mehg"),
    Ident = c(NA,NA,"Op_en3104/pcddf_mean","Op_en4004/conc_mehg_allfish")),
  formula = function(...){
    conc_vit <- oapply(conc_vit, cols=c("Kala", "Adjust"),FUN=mean)
    colnames(conc_vit@output)[colnames(conc_vit@output)=="Nutrient"] <- "Compound"

    conc_pfas <- oapply(conc_pfas, cols=c("Obs","Area"), FUN=mean)
    conc_pfas$Compound[conc_pfas$Compound %in% c("PFOA","PFNA","PFHxS","PFOS")] <- "PFAS"
    conc_pfas <- oapply(conc_pfas, cols="", FUN=sum)
    
    conc_pcddf$Compound <- "TEQ"
    
    conc_mehg <- oapply(conc_mehg[conc_mehg$Area=="Porvoo",], NULL, mean, c("Area","Kala")) # UPDATE FOR PROBABILISTIC APPROACH
    conc_mehg$Compound <- "MeHg"
    
    out <- OpasnetUtils::combine(conc_vit, conc_pfas, conc_pcddf, conc_mehg)
    return(out)
  }
)

#conc <- EvalOutput(conc, verbose=TRUE)
#View(conc@output)
#View(conc_pcddf@output)
#View(conc_mehg@output)

```

```{r exposure}
###################################################################
# Code copied from http://en.opasnet.org/w/Goherr_assessment#

mc2dparam<- list(
  N2 = 10, # Number of iterations in the new Iter
  strength = 50, # Sample size to which the fun is to be applied. Resembles number of observations
  run2d = FALSE, # Should the mc2d function be used or not?
  info = 1, # Ovariable that contains additional indices, e.g. newmarginals.
  newmarginals = c("Exposure"), # Names of columns that are non-marginals but should be sampled enough to become marginals
  method = "bootstrap", # which method to use for 2D Monte Carlo? Currently bootsrap is the only option.
  fun = mean # Function for aggregating the first Iter dimension.
)

if(FALSE) {
## Exposure with background exposure but without mother's exposure to child

expo_dir <- Ovariable(
  "expo_dir",
  dependencies=data.frame(Name=c("amount","conc","expo_bg")),
  formula = function(...) {
    out <- conc[conc$Exposure_agent=="TEQ",] * 0 + 1
    out$Exposure_agent <- "Fish"
    out <- combine(conc, out, name="conc")
    out <- oapply(amount * out, cols="Fish", FUN=sum)
    out <- Ovariable(output = data.frame(
      Exposcen = c("BAU", "No exposure"),
      Result = c(1, 0)
    ), marginal=c(TRUE,FALSE)) * out + expo_bg
    out$Exposure <- as.factor(
      ifelse(
        out$Exposure_agent %in% c("DHA", "MeHg"),
        "To child",
        "To eater"
      )
    )
    return(out)
  },
  unit = "PCDDF, PCB, TEQ: pg /d; Vitamin D, MeHg: µg /d; DHA, EPA, Omega3: mg /d; Fish: g /d"
)

## Background-exposure to vitamin D and omega-3
addexposure <- Ovariable(
  "addexposure",
  ddata = "Op_en7748", # [[Benefit-risk assessment of Baltic herring and salmon intake]]
  subset = "Background exposure",
  unit = "PCDDF, PCB, TEQ: pg /d; Vitamin D, MeHg: µg /d; DHA, EPA, Omega3: mg /d"
)

# Should the background be specific for gender and country? At the moment it is.
expo_bg <- Ovariable(
  "expo_bg",
  dependencies = data.frame(Name="addexposure","info"),
  formula = function(...) {
    out <- addexposure
    
    # Empty values ("") in indices must be replaced by NA so that Ops works correctly.
    levels(out$Gender)[levels(out$Gender) == ""] <- NA
    levels(out$Country)[levels(out$Country) == ""] <- NA
    levels(out$Exposure_agent)[levels(out$Exposure_agent) == ""] <- NA
    out@output <- fillna(out@output, c("Country", "Gender", "Exposure_agent"))
    
    temp1 <- out[out$Exposure_agent %in% c("PCDDF","PCB") , ]
    temp1 <- oapply(temp1, cols = "Exposure_agent", FUN = sum)
    temp1$Exposure_agent <- "TEQ"
    
    temp2 <- out[out$Exposure_agent %in% c("EPA", "DHA") , ]
    temp2 <- oapply(temp2, cols = "Exposure_agent", FUN = sum)
    temp2$Exposure_agent <- "Omega3"
    
    out <- OpasnetUtils::combine(out, temp1, temp2)
    out <- unkeep(out * info, prevresults = TRUE, sources = TRUE)
    
    return(out)
  },
  unit = "PCDDF, PCB, TEQ: pg /d; Vitamin D, MeHg: µg /d; DHA, EPA, Omega3: mg /d"
)

# Stores non-marginal columns for further use.
info <- Ovariable(
  "info",
  dependencies = data.frame(Name = c("jsp")),
  formula = function(...) {
    out <- jsp
    out$Group <- factor(
      paste(out$Gender, out$Ages),
      levels = c("Female 18-45", "Male 18-45", "Female >45", "Male >45")
    )
    out$Country <- factor(out$Country, ordered=FALSE)
    out <- unique(out@output[c("Iter","Country","Group","Gender","Row")])
    out$Result <- 1
    return(out)
  }
)

} # END IF
############################### Code from Goherr assessment ends

expo_dir <- Ovariable(
  "expo_dir",
  dependencies = data.frame(Name=c("conc", "amount")),
  formula = function(...) {
    
    conc$Fish[conc$Fish %in% c("Perch","Pike-perch","Eel","")] <- "Average fish"
    conc <- oapply(conc, cols="", FUN=mean)
    out <- conc * amount 
    
#    colnames(out@output)[colnames(out@output)=="Nutrient"] <- "Exposure_agent"
      
    return(out)
  },
  unit="ng/d"
)

exposure <- Ovariable(
  "exposure",
  dependencies = data.frame(
    Name = c(
      "expo_dir", # direct exposure, i.e. the person eats or breaths the exposure agent themself
      "expo_indir", # indirect exposure, i.e. the person (typically fetus or infant) is exposed via someone else (mother)
      "mc2d" # 2D Monte Carlo function
    ),
    Ident = c(
      NA,
      "Op_en7797/expo_indir2", # [[Infant's dioxin exposure]] # expo_indir
      "Op_en7805/mc2d") # [[Two-dimensional Monte Carlo]]
  ),
  formula = function(...) {
    out <- OpasnetUtils::combine(expo_dir, expo_indir)
    out <- unkeep(out, "Source.1", sources=TRUE)
    out <- mc2d(out)
    out$Exposure[is.na(out$Exposure)] <- "Direct"
    return(out)
  },
  unit = "PCDDF, PCB, TEQ: (To eater: pg /day; to child: pg /g fat); Vitamin D, MeHg: µg /day; DHA, EPA, Omega3: mg /day"
)

exposure <- Ovariable(
  "exposure",
  dependencies=data.frame(Name=c("amount","conc")),
  formula = function(...) {
    out <- amount * conc
    colnames(out@output)[colnames(out@output)=="Compound"] <- "Exposure_agent"
    return(out)
  }
)

```

```{r modelrun}
objects.latest("Op_en2261",code_name="BoDattr2") # [[Health impact assessment]]
tryCatch(BoDattr <- EvalOutput(BoDattr, verbose=TRUE))

```

```{r summary tables}
oprint(summary(amount,"mean"))
oprint(summary(BoD,marginals=c("Age","Response"),"mean"))
oprint(summary(BoDattr,marginals=c("Age","Response"),"mean"))
oprint(summary(BoDattr,marginals=c("Exposure_agent","Response"),"mean"))
oprint(summary(BoDattr,marginals=c("Gender","Response"),"mean"))
oprint(summary(case_burden,"mean"))
oprint(summary(conc,"mean"))
oprint(summary(dose,"mean"))
oprint(summary(ERF,"mean"))
oprint(summary(expo_dir,"mean"))
#oprint(summary(exposure,"mean"))
#oprint(summary(fish_proportion,"mean"))
oprint(summary(incidence,"mean"))
oprint(summary(PAF,"mean"))
oprint(summary(population,"mean"))
oprint(summary(RR,"mean"))

```


```{r plots}
###################
# Graphs
trim <- function(ova) return(oapply(ova, NULL, mean, "Iter")@output)

ggplot(amount@output, aes(x=Gender, weight=amountResult, fill=Kala))+geom_bar()+
  labs(
    title="Kalansyönti Suomessa ikäryhmittäin",
    y="Syönti (g/d)"
  )
ggsave("Kalansyönti Suomessa ikäryhmittäin.svg")

plot_ly(trim(total_amount), x=~Kala, y=~total_amountResult, color=~Kala, type="bar") %>%
  layout(yaxis=list(title="Kalan kokonaiskulutus Suomessa (milj kg /a)"), barmode="stack")

plot_ly(trim(conc_vit), x=~Nutrient, y=~conc_vitResult, color=~Kala, type="scatter", mode="markers") %>%
  layout(yaxis=list(title="Concentrations of nutrients (mg or ug /g)"))

ggplot(conc_pfas@output, aes(x=Fish, y=conc_pfasResult))+geom_point()+ # Inputed data for missing species.
  coord_flip()

ggplot(conc_pfas@output, aes(x=conc_pfasResult, color=Compound, linetype=Area))+stat_ecdf()+
  scale_x_log10()+
  stat_ecdf(data=conc_eukalat@output, aes(x=conc_eukalatResult))+
  scale_linetype_manual(values=c("dotted","solid","twodash"))+
  labs(
    title="PFAS concentration in fishes in Finland",
    x="PFAS concentration (ng/g fresh weight)",
    y="Cumulative probability"
  )
# The code may produce some negative values, which are removed from the graph
ggsave("PFAS-pitoisuus kalassa Suomessa.svg")

ggplot(conc@output, aes(x=concResult, colour=Fish))+stat_ecdf()+
  facet_wrap(~Compound, scales="free_x")

#ggplot(oapply(expo_dir, cols=c("Iter"),FUN=mean)@output,
#       aes(x=Gender, weight=expo_dirResult,fill=Fish))+geom_bar()+
#  facet_wrap(~Compound, scales="free_y")+
#  labs(title="Eri yhdisteiden saanti kalasta")
#ggsave("Yhdisteiden saanti kalasta Suomessa.svg")

plot_ly(trim(exposure), x=~Gender, y=~exposureResult, color=~Exposure_agent, text=~Exposure_agent, type="bar") %>%
  layout(yaxis=list(title="Exposure to nutrients (g or ug /d)"))

ggplot(trim(exposure), aes(x=Gender, weight=exposureResult, fill=Gender))+geom_bar()+
  facet_wrap(~Exposure_agent, scales="free_y")+
  labs(
    title="Exposure to compounds",
    y="(omega: mg/d; vit D: ug/d, PFAS: ng/d)"
  )

cat("Kalaperäisiä tautitaakkoja Suomessa\n")

if(openv$N>1) {
  tmp <- summary(oapply(BoDattr,NULL,sum,c("Age","Gender","Response")))
  tmp <- data.frame(
    Altiste = tmp$Exposure_agent,
    Vaikutus = tmp$Response,
    Keskiarvo = as.character(signif(tmp$mean,2)),
    "95 luottamusväli" = paste0(signif(tmp$Q0.025,2)," - ", signif(tmp$Q0.975,2)),
    Keskihajonta = signif(tmp$sd,2)
  )#[rev(match(lev, tmp$Exposure_agent)),]

  oprint(tmp)
  
  tmp <- summary(oapply(BoDattr,NULL,sum,c("Age","Gender","Exposure_agent")))
  tmp <- data.frame(
    Terveysvaikutus = tmp$Response,
    Keskiarvo = signif(tmp$mean,2),
    "95 luottamusväli" = paste0(signif(tmp$Q0.025,2)," - ", signif(tmp$Q0.975,2)),
    Keskihajonta = signif(tmp$sd,2)
  )
  oprint(tmp)
}

ggplot(trim(BoDattr), aes(x=Exposure_agent, weight=BoDattrResult, fill=Response))+geom_bar()

ggplot(trim(BoDattr), aes(x=Response, weight=BoDattrResult, fill=Exposure_agent))+geom_bar()

ggplot(trim(BoDattr), aes(x=Age, weight=BoDattrResult, fill=Response))+geom_bar(position="stack")

plot_ly(trim(BoDattr), x=~Exposure_agent, y=~BoDattrResult, color=~Response, text=~paste(Age, Exposure_agent, sep=": "), type="bar") %>%
  layout(yaxis=list(title="Disease burden (DALY /a); CHD2=coronary heart disease"), barmode="stack")

################ Insight network
gr <- scrape(type="assessment")
objects.latest("Op_en3861", "makeGraph") # [[Insight network]]
gr <- makeGraph(gr)
#export_graph(gr, "ruori.svg")
#render_graph(gr) # Does not work: Error in generate_dot(graph) : object 'attribute' not found
##################### Diagnostics
objects.latest("Op_en6007", code_name="diagnostics")
showLoctable()
showind()

```