---
title: "Fish and health with national fish promotion programme"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

This is an open assessment looking at potential health effects of a national fish promotion program in Finland. The details of the assessment are described at [Opasnet](http://fi.opasnet.org/fi/PFAS-yhdisteiden tautitaakka). This file contains the R code to run the assessment model.

Knit to html for best performance.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
```

Calculation is based on BONUS GOHERR project and its [http://en.opasnet.org/w/Goherr_assessment](fish health benefit-risk assessment).

What needs to be done for PFAS assessment?

1. Amount should be gender and age-specific, because we need to worry about young mothers. Solution: take KKE amounts of fish, and scale those with the Goherr subgroup-specific proportions. DONE
2. Amounts should reflect the actual fish consumption in Porvoo. Solution: postpone and use national statistics. DONE
3. Infant's dioxin concentration module must be added. Solution: Use Goherr model for expo_indir DONE
4. The module must be updated to match PFAS as well. Solution: update the module to contain column Exposure_agent. Change body fat parameter to volume of distribution.
4. Find why expo_indir is so much higher than EFSA toxicokinetic assessment.
5. Add ERF for PFAS (sum of PFOS, PFHxS, PFOA, PFNA). Solution: Make a new page for ERF of PFAS and add that to adjusted ERFs. First immunology; postpone cholesterol and low birth weight and liver toxicity.
6. Add case burdens for PFAS outcomes. Solution: give rough estimates for immunology to get started.
7. Add PFAS concentrations to data. Solution: Look at Porvoo concentrations first and make Inpconc.


```{r downloads}
# This code was forked from https://github.com/jtuomist/fishhealth/blob/master/fishhealth.Rmd
# This code was previously forked from code Op_fi5923/model on page [[Kotimaisen kalan edistämisohjelma]]
# The code was even more previously forked from Op_fi5889/model on page [[Ruori]] and Op_en7748/model on page [[Goherr assessment]]

library(OpasnetUtils) # Install the newest version from https://github.com/jtuomist/OpasnetUtils not from CRAN.
library(tidyverse)
library(plotly)

# First empty all objects for a fresh start. Otherwise may be problems with CheckDecisions.
oempty(all=TRUE)
openv.setN(10)

dat <- opbase.data("Op_fi5932", subset="Malliparametrit")[-1] # [[PFAS-yhdeisteiden tautitaakka]]
dec <- opbase.data("Op_fi5932", subset="Decisions")[-1]
DecisionTableParser(dec)

CTable <- opbase.data("Op_fi5932",subset="CollapseMarginals")
for(i in 1:ncol(CTable)) {CTable[[i]] <- as.character(CTable[[i]])}
CollapseTableParser(CTable)

objects.latest("Op_en2031", code_name="subgrouping") # [[Exposure-response function]] subgrouping

cat("Laskennassa käytetty data.\n")
dat
cat("Tarkastellut päätökset.\n")
dec
cat("Aggregoidut marginaalit.\n")
CTable

#' prepare adjusts the data table for ovariables. Requires function subgrouping from code Op_en2031/initiate on page [[Exposure-response function]]
#' @param dat data.frame
#' @param type type of data that is used. Must match content in column Type
#' @param drop columns to remove
#' @return data.frame
prepare <- function(dat, type=NULL, drop=NULL) {
  out <- dat
  if(!is.null(type)) out <- out[out$Type %in% type , ]
  if(!is.null(drop)) out <- out[!colnames(out) %in% drop]
  return(subgrouping(out))
}

dummy <- Ovariable("summy",data=data.frame(Age="dummy", Result=1))

fish_proportion <- Ovariable( # How age groups eat fish differently
  "fish_proportion",
  dependencies = data.frame(Name="dummy"),
  formula = function(...) {
    out = prepare(dat,"fish_proportion",c("Type","Exposure_agent","Response","Unit"))
    out$Result <- as.numeric(as.character(out$Result))
    out$Result <- out$Result / sum(out$Result) * length(out$Result)
    return(out)
  },
  unit="-")

amount <- Ovariable(
  "amount",
  dependencies = data.frame(Name="fish_proportion"),
  formula = function(...) {
    amount = Ovariable("total_amount", data=prepare(dat, "amount", c("Type","Response","Exposure_agent","Unit")))
      # Filleted weight, i.e. no loss.
    amount <- amount * 1000 / 5.52 /365.25 
      # M kg/a per 5.52M population --> g/d per average person.
    amount <- amount * fish_proportion
      # fish_proportion tells the relative amount in each subgroup
  
    # Match KKE-classification in amount with Fineli classification
    tmp <- Ovariable(
      output = data.frame(
        Kala = c("Kasvatettu", "Kaupallinen", "Kirjolohi", "Silakka", "Vapaa-ajan", "Muu tuonti", "Tuontikirjolohi", "Tuontilohi"),
        Fish = c("Whitefish", "Average fish","Rainbow trout", "Herring", "Average fish", "Average fish", "Rainbow trout", "Salmon"),
        Result = 1
      ),
      marginal = c(TRUE, TRUE, FALSE)
    )
    
    amount <- amount * tmp
    
    return(amount)
  },
  unit="g/d"
)
# Exposure:To child and To eater not needed, because dioxins are not (yet) included

amount <- EvalOutput(amount)
ggplot(amount@output, aes(x=Age, weight=amountResult, fill=Kala))+geom_bar()+
  labs(
    title="Kalansyönti Suomessa ikäryhmittäin",
    y="Syönti (g/d)"
  )
ggsave("Kalansyönti Suomessa ikäryhmittäin.svg")

population <- Ovariable(
  "population",
  data = prepare(dat,"population",c("Type","Exposure_agent","Response","Unit")),
  unit="#")
#exposure <- Ovariable("exposure", data = prepare(dat, "exposure", c("Type","Response")))
#frexposed <- Ovariable("frexposed", data=prepare(dat, "frexposed", c("Type","Response","Unit")))

incidence <- Ovariable(
  "incidence",
  data = prepare(dat,"incidence",c("Type","Exposure_agent","Unit")),
  unit="1/person-year")

```

```{r concentrations}

conc_vit <- Ovariable(
  "conc_vit",
  ddata = "Op_en1838", # [[Concentrations of beneficial nutrients in fish]]
  subset = "Fineli data for common fish species"
)
  df = conc_vit@data
  df$Nutrient[df$Nutrient=="D-vitamiini (µg)"] <- "Vitamin D"
  df$Nutrient[df$Nutrient=="rasvahapot n-3 moni-tyydyttymättömät (g)"] <- "Omega3"
  df$Nutrient[df$Nutrient=="rasvahappo 18:3 n-3 (alfalinoleenihappo) (mg)"] <- "ALA"
  df$Nutrient[df$Nutrient=="rasvahappo 22:6 n-3 (DHA) (mg)"] <- "DHA"
  df$Nutrient[df$Nutrient=="proteiini (g)"] <- "Fish"
  df$conc_vitResult[df$Nutrient=="Fish"] <- "1"
  df <- dropall(df[df$Nutrient %in% c("Vitamin D", "Omega3", "ALA", "DHA", "Fish") , ])
conc_vit@data <- df

######## Concentration of PFAS

# Data from EU-kalat3 (Finland excl Vanhankaupunginlahti): # pg/g fresh weight
#       POP     mean       sd      min   Q0.025   median   Q0.975      max
# 2.5% PFOS 2055.757 1404.045 305.0399 330.1365 1533.269 5029.697 5814.935

# Data from EU-kalat3 (Vanhankaupunginlahti, Helsinki) # ng/g f.w.
#      POP   mean       sd      min   Q0.025   median   Q0.975      max
#2.5% PFOS 14.428 11.94542 1.499441 1.607789 15.64988 35.32517 38.91994

conc_eukalat <- EvalOutput(Ovariable(
  "conc_eukalat",
  data = data.frame(
    Area = c("Suomi","Helsinki"),
    Compound="PFOS",
    Result=c("2.056 (3.301 - 5.030)", "14.428 (1.499 - 35.325)")),
  unit="ng/g fresh weight"
))

conc_pfas <- Ovariable(
  "conc_pfas",
  data=opbase.data("Op_fi5932",subset="PFAS concentrations"),
  unit="ng/g fresh weight")
conc_pfas@data$Area <- "Porvoo"
conc_pfas <- EvalOutput(conc_pfas)

ggplot(conc_pfas@output, aes(x=conc_pfasResult, color=Compound, linetype=Area))+stat_ecdf()+
  scale_x_log10()+
  stat_ecdf(data=conc_eukalat@output, aes(x=conc_eukalatResult))+
  scale_linetype_manual(values=c("dotted","solid","twodash"))+
  labs(
    title="PFAS concentration in fishes in Finland",
    x="PFAS concentration (ng/g fresh weight)",
    y="Cumulative probability"
  )
# The code may produce some negative values, which are removed from the graph
ggsave("PFAS-pitoisuus kalassa Suomessa.svg")

sum_pfas <- oapply(conc_pfas, cols=c("Kala","Compound"), FUN=sum)
tmp <- conc_pfas / sum_pfas
summary(tmp, marginals="Compound")

## This tells that PFOS consists of 71 - 97 % of the four key PFAS, while PFOA, PFNA, and PFHxS consist of 
# 0 - 10 %, 2 - 18 %, and 0 - 9 %, respectively.
# Even if we included the next most abundant congeners, i.e. PFDA and PFUnA, the overall picture would not change.

conc <- Ovariable(
  "conc",
  dependencies = data.frame(Name="conc_vit", "conc_pfas"),
  formula = function(...){
    conc_vit <- oapply(conc_vit, cols=c("Kala", "Adjust"),FUN=mean)
    colnames(conc_vit@output)[colnames(conc_vit@output)=="Nutrient"] <- "Compound"

    conc_pfas <- oapply(conc_pfas, cols=c("Obs","Area"), FUN=mean)
    conc_pfas$Compound[conc_pfas$Compound %in% c("PFOA","PFNA","PFHxS","PFOS")] <- "PFAS"
    conc_pfas <- oapply(conc_pfas, cols="", FUN=sum)
    
    out <- OpasnetUtils::combine(conc_vit, conc_pfas)
    return(out)
  }
)
conc <- EvalOutput(conc)

ggplot(conc@output, aes(x=concResult, colour=Fish))+stat_ecdf()+
  facet_wrap(~Compound, scales="free_x")

```

```{r exposure}
###################################################################
# Code copied from http://en.opasnet.org/w/Goherr_assessment#

mc2dparam<- list(
  N2 = 1000, # Number of iterations in the new Iter
  strength = 50, # Sample size to which the fun is to be applied. Resembles number of observations
  run2d = FALSE, # Should the mc2d function be used or not?
  info = 1, # Ovariable that contains additional indices, e.g. newmarginals.
  newmarginals = c("Group","Exposure"), # Names of columns that are non-marginals but should be sampled enough to become marginals
  method = "bootstrap", # which method to use for 2D Monte Carlo? Currently bootsrap is the only option.
  fun = mean # Function for aggregating the first Iter dimension.
)

if(FALSE) {
## Exposure with background exposure but without mother's exposure to child

expo_dir <- Ovariable(
  "expo_dir",
  dependencies=data.frame(Name=c("amount","conc","expo_bg")),
  formula = function(...) {
    out <- conc[conc$Exposure_agent=="TEQ",] * 0 + 1
    out$Exposure_agent <- "Fish"
    out <- combine(conc, out, name="conc")
    out <- oapply(amount * out, cols="Fish", FUN=sum)
    out <- Ovariable(output = data.frame(
      Exposcen = c("BAU", "No exposure"),
      Result = c(1, 0)
    ), marginal=c(TRUE,FALSE)) * out + expo_bg
    out$Exposure <- as.factor(
      ifelse(
        out$Exposure_agent %in% c("DHA", "MeHg"),
        "To child",
        "To eater"
      )
    )
    return(out)
  },
  unit = "PCDDF, PCB, TEQ: pg /d; Vitamin D, MeHg: µg /d; DHA, EPA, Omega3: mg /d; Fish: g /d"
)

## Background-exposure to vitamin D and omega-3
addexposure <- Ovariable(
  "addexposure",
  ddata = "Op_en7748", # [[Benefit-risk assessment of Baltic herring and salmon intake]]
  subset = "Background exposure",
  unit = "PCDDF, PCB, TEQ: pg /d; Vitamin D, MeHg: µg /d; DHA, EPA, Omega3: mg /d"
)

# Should the background be specific for gender and country? At the moment it is.
expo_bg <- Ovariable(
  "expo_bg",
  dependencies = data.frame(Name="addexposure","info"),
  formula = function(...) {
    out <- addexposure
    
    # Empty values ("") in indices must be replaced by NA so that Ops works correctly.
    levels(out$Gender)[levels(out$Gender) == ""] <- NA
    levels(out$Country)[levels(out$Country) == ""] <- NA
    levels(out$Exposure_agent)[levels(out$Exposure_agent) == ""] <- NA
    out@output <- fillna(out@output, c("Country", "Gender", "Exposure_agent"))
    
    temp1 <- out[out$Exposure_agent %in% c("PCDDF","PCB") , ]
    temp1 <- oapply(temp1, cols = "Exposure_agent", FUN = sum)
    temp1$Exposure_agent <- "TEQ"
    
    temp2 <- out[out$Exposure_agent %in% c("EPA", "DHA") , ]
    temp2 <- oapply(temp2, cols = "Exposure_agent", FUN = sum)
    temp2$Exposure_agent <- "Omega3"
    
    out <- combine(out, temp1, temp2)
    out <- unkeep(out * info, prevresults = TRUE, sources = TRUE)
    
    return(out)
  },
  unit = "PCDDF, PCB, TEQ: pg /d; Vitamin D, MeHg: µg /d; DHA, EPA, Omega3: mg /d"
)

# Stores non-marginal columns for further use.
info <- Ovariable(
  "info",
  dependencies = data.frame(Name = c("jsp")),
  formula = function(...) {
    out <- jsp
    out$Group <- factor(
      paste(out$Gender, out$Ages),
      levels = c("Female 18-45", "Male 18-45", "Female >45", "Male >45")
    )
    out$Country <- factor(out$Country, ordered=FALSE)
    out <- unique(out@output[c("Iter","Country","Group","Gender","Row")])
    out$Result <- 1
    return(out)
  }
)

} # END IF
############################### Code from Goherr assessment ends

expo_dir <- Ovariable(
  "expo_dir",
  dependencies = data.frame(Name=c("conc", "amount")),
  formula = function(...) {
    
    conc$Fish[conc$Fish %in% c("Perch","Pike-perch","Eel","")] <- "Average fish"
    conc <- oapply(conc, cols="", FUN=mean)
    out <- conc * amount 
    
#    colnames(out@output)[colnames(out@output)=="Nutrient"] <- "Exposure_agent"
      
    return(out)
  },
  unit="ng/d"
)

expo_dir <- EvalOutput(expo_dir)
View(expo_dir@output)
ggplot(oapply(expo_dir, cols=c("Iter"),FUN=mean)@output,
       aes(x=Age, weight=expo_dirResult,fill=Fish))+geom_bar()+
  facet_wrap(~Compound, scales="free_y")+
  labs(title="Eri yhdisteiden saanti kalasta")
ggsave("Yhdisteiden saanti kalasta Suomessa.svg")

#objects.latest("Op_en7797", code_name="expo_indir2") # [[Infant's dioxin exposure]] expo_indir, t0.5, f_ing, f_mtoc, BF

exposure <- Ovariable(
  "exposure",
  dependencies = data.frame(
    Name = c(
      "expo_dir", # direct exposure, i.e. the person eats or breaths the exposure agent themself
      "expo_indir", # indirect exposure, i.e. the person (typically fetus or infant) is exposed via someone else (mother)
      "mc2d" # 2D Monte Carlo function
    ),
    Ident = c(
      NA,
      "Op_en7797/expo_indir2", # [[Infant's dioxin exposure]] # expo_indir
      "Op_en7805/mc2d") # [[Two-dimensional Monte Carlo]]
  ),
  formula = function(...) {
    out <- OpasnetUtils::combine(expo_dir, expo_indir)
    out <- unkeep(out, "Source.1", sources=TRUE)
    out <- mc2d(out)
    out$Exposure[is.na(out$Exposure)] <- "Direct"
    return(out)
  },
  unit = "PCDDF, PCB, TEQ: (To eater: pg /day; to child: pg /g fat); Vitamin D, MeHg: µg /day; DHA, EPA, Omega3: mg /day"
)

exposure <- EvalOutput(exposure)
View(exposure@output)

ggplot(exposure@output, aes(x=Age, weight=exposureResult, fill=Fish))+geom_bar()+
  facet_grid(Compound~Exposure, scales="free_y")+
  labs(
    title="Exposure to compounds",
    y="(omega: mg/d; vit D: ug/d, PFAS: ng/d)"
  )

InpERF <- Ovariable(
  "InpERF",
  data = prepare(dat,"InpERF",c("Unit")),
  unit="ng/kg/wk")
InpERF <- EvalOutput(InpERF)

Inpcase_burden <- Ovariable(
  "Inpcase_burden",
  data = prepare(dat,"Inpcase_burden",c("Exposure_agent","Unit")),
  unit="DALY/case")
Inpcase_burden <- EvalOutput(Inpcase_burden)

# Incidence-based data not needed
frexposed <- 1
incidence <- 1
ERFchoice <- Ovariable(
  "ERFchoice",
  data=data.frame(
    Response=c("Loss in child's IQ points","CHD2 mortality","Breast cancer","All-cause mortality","Depression","Immunosuppression"),
    Exposure_agent=c("DHA","Omega3","Omega3","Fish","Fish","PFAS"),
    Result=1)
)
case_burden <- Ovariable("case_burden", data= prepare(dat,"case burden",c("Type","Exposure_agent","Unit")))
objects.latest("Op_en5917", code_name="InpBoD") # [[Disease risk]] InpBoD for GOHERR
InpBoD <- EvalOutput(InpBoD) # Evaluated because is not a dependency but an Input
InpBoD <- InpBoD[InpBoD$Country=="FI",colnames(InpBoD@output)!="Country"]
```

```{r modelrun}
objects.latest("Op_en2261",code_name="BoDattr2") # [[Health impact assessment]]
tryCatch(BoDattr <- EvalOutput(BoDattr, verbose=TRUE))
```


```{r plots}
###################
# Graphs
trim <- function(ova) return(oapply(ova, NULL, mean, "Iter")@output)
plot_ly(trim(amount), x=~Scenario, y=~amountResult, color=~Kala, type="bar") %>%
  layout(yaxis=list(title="Kalan kokonaiskulutus Suomessa (milj kg /a)"), barmode="stack")
plot_ly(trim(conc_vit), x=~Nutrient, y=~conc_vitResult, color=~Kala, type="scatter", mode="markers") %>%
  layout(yaxis=list(title="Concentrations of nutrients (mg or ug /g)"))
tmp <- exposure / Ovariable(
  output = data.frame(
    Exposure_agent = c("Fish","Vitamin D", "Omega3", "ALA", "DHA"),
    Result = c(1, 1, 1000, 1000, 1000)
  ), marginal = c(TRUE, FALSE)
)
plot_ly(trim(tmp), x=~Scenario, y=~Result, color=~Exposure_agent, text=~Exposure_agent, type="bar") %>%
  layout(yaxis=list(title="Exposure to nutrients (g or ug /d)"))
summary(conc_vit, "mean")
summary(exposure,"mean")
summary(amount,"mean")
summary(BoD,"mean")
summary(BoDattr,"mean")
cat("Kalaperäisiä tautitaakkoja Suomessa\n")
tmp <- summary(oapply(BoDattr,NULL,sum,"Group")[BoDattr$Scenario=="BAU",])
data.frame(
  Altiste = tmp$Exposure_agent,
  Vaikutus = tmp$Response,
  Keskiarvo = as.character(signif(tmp$mean,2)),
  "95 luottamusväli" = paste0(signif(tmp$Q0.025,2)," - ", signif(tmp$Q0.975,2)),
  Keskihajonta = signif(tmp$sd,2)
)#[rev(match(lev, tmp$Exposure_agent)),]
ggplot(trim(BoDattr), aes(x=Scenario, weight=BoDattrResult, fill=Response))+geom_bar()
ggplot(trim(BoDattr), aes(x=Scenario, weight=BoDattrResult, fill=Exposure_agent))+geom_bar()
plot_ly(trim(BoDattr), x=~Scenario, y=~BoDattrResult, color=~Response, text=~paste(Group, Exposure_agent, sep=": "), type="bar") %>%
  layout(yaxis=list(title="Disease burden (DALY /a); CHD2=coronary heart disease"), barmode="stack")
tmp <- summary(oapply(BoDattr,NULL,sum,c("Age","Exposure_agent")))
data.frame(
  Altiste = tmp$Response,
  Keskiarvo = signif(tmp$mean,2),
  "95 luottamusväli" = paste0(signif(tmp$Q0.025,2)," - ", signif(tmp$Q0.975,2)),
  Keskihajonta = signif(tmp$sd,2)
)
################ Insight network
gr <- scrape(type="assessment")
objects.latest("Op_en3861", "makeGraph") # [[Insight network]]
gr <- makeGraph(gr)
#export_graph(gr, "ruori.svg")
render_graph(gr)
##################### Diagnostics
objects.latest("Op_en6007", code_name="diagnostics")
showLoctable()
showind()
```